TBD

### 2021-02-14 outputs/paper/paper.Rmd
Add stratified sampling

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
```

```{r, include=FALSE}
#### Global Functions ####
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}

```

@@

```{r, echo = FALSE}
#### Pie Chart ####

### Import cleaned business licences dataset
dfCleanBiz <- readr::read_csv("../../inputs/data/clean_business_licences.csv")

### Create data frame
dfBoroughs <- data.frame(
  group = dfCleanBiz$fsa,
  value = dfCleanBiz$n
)

### Calculate percentages
dfBoroughs <- dfBoroughs %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(dfBoroughs$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop ) %>%
  arrange(desc(prop))

# print(dfBoroughs)

### Create pie chart
ggplot(dfBoroughs, aes(x="", y = prop, fill = group)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  theme_void() + 
  geom_text(aes(y = ypos, label = percent(prop)), color = "white", size=3) +
  scale_fill_brewer(palette = "Paired")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
```

```{r, include=FALSE}
#### Global Functions ####
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}
```

@@

```{r, echo = FALSE}
#### Pie Chart ####
### Import cleaned business licences dataset
dfCleanBiz <- readr::read_csv("../../inputs/data/clean_business_licences.csv")
### Create data frame
dfBoroughs <- data.frame(
  group = dfCleanBiz$fsa,
  value = dfCleanBiz$n
)
### Calculate percentages
dfBoroughs <- dfBoroughs %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(dfBoroughs$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop ) %>%
  arrange(desc(prop))
# print(dfBoroughs)
### Create pie chart
ggplot(dfBoroughs, aes(x="", y = prop, fill = group)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  theme_void() + 
  geom_text(aes(y = ypos, label = percent(prop)), color = "white", size=3) +
  scale_fill_brewer(palette = "Paired")
```

```{r, echo = FALSE}
print(dfBoroughs$prop)
```
